\section*{Question 2}

Search and list a few IO devices that are interfaced over a UART.\@
Provide one or two lines description for each.

\subsection*{Solution}

\subsubsection*{GPS module}

A GPS module is a device that receives signals from satellites to determine the device's location.
They communicate via UART, sending serial data with position, speed, and time information.

\subsubsection*{Bluetooth module}

A Bluetooth module is a device that enables wireless communication between devices.
Commonly interfaced via UART, these modules can connect to smartphones, computers, or other peripherals, enabling features like file transfer, audio streaming, and remote control.

\subsubsection*{RFID reader}

An RFID reader is a device that reads data from RFID tags.
Typically interfaced through UART, it transmits data about the detected tags, such as unique identification numbers, to a microcontroller for processing, making it useful for access control, inventory management, and logistics.

\subsubsection*{Wi-Fi \& Ethernet modules}

Wi-Fi and Ethernet modules are devices that enable wireless and wired communication, respectively.
Wi-Fi modules enable devices to connect to wireless networks for internet access. When interfaced over UART, they can send and receive data packets, allowing microcontrollers to communicate with web servers, cloud services, or other networked devices, making them essential for IoT applications.

\subsubsection*{Modem}

A modem converts digital signals from a computer into analog signals for transmission over telephone lines and vice versa.
When interfaced via UART, it allows devices to connect to the internet or other networks, enabling data communication over long distances.
